### 2016-01-29 paper/main.tex
update paper

With this in place, the penalized log-likelihood for $\pi$ is given by:
\begin{equation}
\log L(\pi) + \log h(\pi) = \sum_{j=1}^n \log(\sum_{k=0}^K \pi_k l_{kj}) + \sum_{k=0}^K (\lambda_k-1) \log \pi_k
\end{equation}
where the $l_{kj}:= \tilde{f}_k(\bhat_j)$ are known. This is a convex optimization problem, which
can be solved very quickly and reliably using interior point (IP) methods. We used the {\tt KWdual} function from the {\tt R} package {\tt REBayes} \cite{REBayes}, which uses {\tt Rmosek} \cite{Rmosek}. We also found a simple EM algorithm \cite{dempster77}, accelerated using the elegant {\tt R} package {\tt SQUAREM} \cite{varadhan2008simple},
to provide adequate performance. In our EM implementation we initialized $\pi_k=1/n$ for $k=1,\dots,K$, with $\pi_0=1-\pi_1-\dots-\pi_K$,
and the one-step updates are:
\begin{align} \label{eqn:w}
w_{kj} & = \pi_k l_{kj} / \sum_{k'} {\pi_{k'} l_{k'j}} \\
n_k & = \sum_j w_{kj} + \lambda_k - 1 \quad \text{[E Step]} \\
\pi_k &= n_k/\sum_{k'} n_{k'} \quad \text{[M step]}.
\end{align}
One benefit to the EM algorithm is fewer software dependencies.
Both EM and IP methods are implemented in the {\tt ashr} package; results shown here are from the IP method, but graphs from EM are essentially the same.
See \href{http://stephenslab.github.io/ash/analysis/checkIP.html}{http://stephenslab.github.io/ash/analysis/checkIP.html}  and \href{http://stephenslab.github.io/ash/analysis/IPvsEM.html}{http://stephenslab.github.io/ash/analysis/checkIP.html}  for comparisons.

>>>>

With this in place, the penalized log-likelihood for $\pi$ is given by:
\begin{equation}
\log L(\pi) + \log h(\pi) = \sum_{j=1}^n \log(\sum_{k=0}^K \pi_k l_{kj}) + \sum_{k=0}^K (\lambda_k-1) \log \pi_k
\end{equation}
where the $l_{kj}:= \tilde{f}_k(\bhat_j)$ are known. This is a convex optimization problem, which
can be solved very quickly and reliably using interior point (IP) methods. We used the {\tt KWdual} function from the {\tt R} package {\tt REBayes} \cite{REBayes}, which uses {\tt Rmosek} \cite{Rmosek}. We also found a simple EM algorithm \cite{dempster77}, accelerated using the elegant {\tt R} package {\tt SQUAREM} \cite{varadhan2008simple},
to provide adequate performance. In our EM implementation we initialized $\pi_k=1/n$ for $k=1,\dots,K$, with $\pi_0=1-\pi_1-\dots-\pi_K$,
and the one-step updates are:
\begin{align} \label{eqn:w}
w_{kj} & = \pi_k l_{kj} / \sum_{k'} {\pi_{k'} l_{k'j}} \\
n_k & = \sum_j w_{kj} + \lambda_k - 1 \quad \text{[E Step]} \\
\pi_k &= n_k/\sum_{k'} n_{k'} \quad \text{[M step]}.
\end{align}
One benefit to the EM algorithm is fewer software dependencies.
Both EM and IP methods are implemented in the {\tt ashr} package; results shown here are from the IP method, but graphs from EM are essentially the same.
See \href{http://stephenslab.github.io/ash/analysis/checkIP.html}{http://stephenslab.github.io/ash/analysis/checkIP.html}  and \href{http://stephenslab.github.io/ash/analysis/IPvsEM.html}{http://stephenslab.github.io/ash/analysis/IPvsEM.html}  for comparisons.
